The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-05-15 ms.tex
Fix typo in header
Change order of authors

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{siunitx}                    ``
\usepackage{newtxtext}
\usepackage[stix2,smallerops]{newtxmath}
\usepackage{booktabs}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}
\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

@@

\author[López et al.]{
  J. A. López,\(^1\)\thanks{
    jal@astro.unam.mx,
    tere@astro.unam.mx,
    w.henney@irya.unam.mx,
    richer@astro.unam.mx
  }
  Ma.\ T. García-Díaz,\(^1\)\footnotemark[1]
  William J. Henney\(^2\)\footnotemark[1]
  and M. G. Richer\(^1\)\footnotemark[1]
  \\
  \(^1\)\foreignlanguage{spanish}{
    Instituto de Astronomía,
    Universidad Nacional Autónoma de México,
    Ensenada, Baja California, 22800, México}
  \\
  \(^2\)\foreignlanguage{spanish}{
    Instituto de Radioastronomía y
    Astrofísica, Universidad Nacional Autónoma de México, Apartado
    Postal 3-72, 58090 Morelia, Michaoacán, Mexico}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

 \begin{figure}
\centering
  \includegraphics[width=0.4\textwidth]{tere-figs/Figure-i+s}
  \caption{ }
\end{figure}

\begin{table}
\centering
%\caption{Log  of Time-resolved  Observations of {\bf NGC~6210}.}
\begin{tabular}{l|cccccccc} \hline 
&  \multicolumn{7}{c}{Spectroscopy hight resolution/ 2.1m  OAN-SPM}            \\[0.1pt]
\hline 
Run    &   Exp. & Range  & Slit & P. A.   & slit        \\
Epoch   &     Time        &    (s)   &  (\AA)    &    (\AA)  & (m$\mu$)     \\[1pt]   \hline 
28/06/1998          & 30 & H$\alpha$  & 150 & 90 & O\\
28/06/1998          & 300 & H$\alpha$  & 150 & 90 & N\\
28/06/1998           & 1200 & H$\alpha$   & 150 & 90 & M,P,Q \\
05/06/2003         & 1800 &  H$\alpha$   & 70 &0 &     B,D,E,F,H,I,K\\ 
16/10/2003   &  1800 &   H$\alpha$    & 70 & $-$21 & T\\
16/10/2003    &  1800 &   H$\alpha$   & 70 & $-$68 & V\\
17/10/2003    &  1800 &   H$\alpha$  & 70 & 77 & W\\
13/06/2004   & 1800 &   O\sc{iii}  & 70 & $-$9 & R  \\  
13/06/2004   & 1800 &   O\sc{iii}  & 70 & $-$19 & S  \\  
14/06/2004    & 1800 &   S\sc{ii} &150 & $-$19 & S  \\
13/06/2004   & 1800 &   O\sc{iii}  & 70 & $-$56 & U  \\  
14/06/2004   & 1800 &   O\sc{iii}  & 150 & 0 & A,L  \\
21/05/2011     & 1800 & H$\alpha$  & 150 & 0 & G \\
21/05/2011     & 600 & O\sc{iii} & 150 & 0  & G \\
06/07/2013    &  1800 & H$\alpha$   & 150 & 0 & C,I,J \\
18/08/2015  &  1800 &   H$\alpha$, [OIII]  & 70 & 0 & C,D,E,F,G\\
19/08/2015  &  1800 &   H$\alpha$, [OIII]   & 70 & 0 & B,A,I\\
20/08/2015   &  1800 &   H$\alpha$, [OIII] & 70 & 0 & H,J,K\\
18/09/2019  &  1800 &   H$\alpha$    & 150 & 56 & \\

>>>>

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{newtxtext}
\usepackage[stix2,smallerops]{newtxmath}
\usepackage{booktabs}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}
\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

@@

\author[López et al.]{
  William J. Henney,\(^1\)\thanks{
    w.henney@irya.unam.mx,
    jal@astro.unam.mx,
    tere@astro.unam.mx,
    richer@astro.unam.mx
  }
  J. A. López\(^2\)\footnotemark[1]
  Ma.\ T. García-Díaz,\(^2\)\footnotemark[1]
  and M. G. Richer\(^2\)\footnotemark[1]
  \\
  \(^1\)\foreignlanguage{spanish}{
    Instituto de Radioastronomía y
    Astrofísica, Universidad Nacional Autónoma de México, Apartado
    Postal 3-72, 58090 Morelia, Michaoacán, Mexico}
  \\
  \(^2\)\foreignlanguage{spanish}{
    Instituto de Astronomía,
    Universidad Nacional Autónoma de México,
    Ensenada, Baja California, 22800, México}
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

 \begin{figure}
\centering
  \includegraphics[width=0.4\textwidth]{tere-figs/Figure2a}
  \caption{ }
\end{figure}

\begin{table}
\centering
%\caption{Log  of Time-resolved  Observations of {\bf NGC~6210}.}
\begin{tabular}{l|cccccccc} \hline 
&  \multicolumn{7}{c}{Spectroscopy hight resolution/ 2.1m  OAN-SPM}            \\[0.1pt]
\hline 
Run    &   Exp. & Range  & Slit & P. A.   & slit        \\
Epoch   &     Time        &    (s)   &  (\AA)    &    (\AA)  & (m$\mu$)     \\[1pt]   \hline 
28/06/1998          & 30 & H$\alpha$  & 150 & 90 & O\\
28/06/1998          & 300 & H$\alpha$  & 150 & 90 & N\\
28/06/1998           & 1200 & H$\alpha$   & 150 & 90 & M,P,Q \\
05/06/2003         & 1800 &  H$\alpha$   & 70 &0 &     A,B,D*,E*,F,H,I,K\\ 
16/10/2003   &  1800 &   H$\alpha$    & 70 & $-$21 & T\\
16/10/2003    &  1800 &   H$\alpha$   & 70 & $-$68 & V\\
17/10/2003    &  1800 &   H$\alpha$  & 70 & 77 & W\\
13/06/2004   & 1800 &   O\sc{iii}  & 70 & $-$9 & R  \\  
13/06/2004   & 1800 &   O\sc{iii}  & 70 & $-$19 & S  \\  
13/06/2004   & 1800 &   O\sc{iii}  & 70 & $-$56 & U  \\  
14/06/2004   & 1800 &   O\sc{iii}  & 150 & 0 & A',L  \\
21/05/2011     & 1800 & H$\alpha$  & 150 & 0 & G* \\
21/05/2011     & 600 & O\sc{iii} & 150 & 0  & G \\
06/07/2013    &  1800 & H$\alpha$   & 150 & 0 & C,I,J \\
18/08/2015  &  1800 &   H$\alpha$, [OIII]  & 70 & 0 & C,D,E,F,G\\
19/08/2015  &  1800 &   H$\alpha$, [OIII]   & 70 & 0 & B,A*,I\\
20/08/2015   &  1800 &   H$\alpha$, [OIII] & 70 & 0 & H,J,K\\
18/09/2019  &  1800 &   H$\alpha$    & 150 & 56 & \\
